---
title: "Reproducible Research - Peer Assigment 1"
author: "Jorge A. Sanchez Nuñez"
date: "Sunday, February 15, 2015"
output: html_document
---

### 1. Loading and Preprocessing the Data

Download
unzip
and load data

```{r}
url <- "https://github.com/josanu/RepData_PeerAssessment1/blob/master/activity.zip"
if (!file.exists("activity.csv")) {
  download.file(url, destfile = "activity.zip")
  unz(unz("activity.zip", "activity.csv"))
}

activity <- read.csv("activity.csv")
```

### 2. Process/transform the data (if necessary) into a format suitable for your analysis

## What is mean total number of steps taken per day ?

```{r}

steps <- aggregate(steps~date,activity,sum)

hist(steps$steps, main = "Total Steps per Day", col="blue", xlab="Number of Steps")

```

## mean and median of the total number of steps taken per day

```{r}

rmean <- mean(steps$steps)
rmedian <- median(steps$steps)
```

The mean is `r rmean` and the median is `r rmedian`

## what is the average daily activity pattern ?

* Calculate average steps for each interval
* Plot the Average Number Steps per Day by Interval
* Find interval with most average steps

```{r}

steps <- aggregate(steps~interval,activity,mean)
plot(steps$interval, steps$steps, type="l", xlab="Interval", ylab="Number of Steps", main="Averge Number of Steps per Day by Interval")
```


```{r}
max <- steps[which.max(steps$steps),1]
```

The maximum number of steps is `r max` for the 5-minute interval

## Impute missing values

Calculate the total number of missing values

```{r}
sum(is.na(activity))
```

```{r}
imputed <- activity[complete.cases(activity),]
head(imputed)
```

Histogram of the total number of steps taken each day




Calculate and report the mean and median total number of steps taken per day.

```{r}

stepsimputedmean <- mean(imputed$steps)
stepsimputedmedian <- median(imputed$steps)
```

* Mean imputed : `r stepsimputedmean`
* Median imputed : `r stepsimputedmedian`

# Are there diferences in activity patterns between weekdays and weekends ?

Create a new factor variable in the dataset (weekday & weekend)

```{r}
imputed$dateType <-  ifelse(as.POSIXlt(imputed$date)$wday %in% c(0,6), 'weekend', 'weekday')


```

the Graph

```{r}
par(mfrow=c(2,1))


for (type in c("weekend", "weekday")) {
    steps.type <- aggregate(steps ~ interval, data = imputed, subset = imputed$dateType == type, FUN = mean)
    plot(steps.type, type = "l", main = type)
}
````